Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2015-09-14 paper.tex
More introduction work

In this study we set out to model the wake of the University of New Hampshire's
Reference Vertical-Axis (cross-flow) Turbine (UNH-RVAT) using a
Reynolds-averaged Navier--Stokes numerical model. Note that studies in the
literature generally focus on predicting the turbine loading and the local blade
flow rather than the turbine wake. In contrast, we seek to model the near-wake
flow.

The wake of this particular turbine is of interest since it has been shown that
the neark-wake's momentum and energy transport processes are dominated by
vertical advection \cite{Bachant2015-JoT}. It logically follows that a 2-D
simulation would not correctly predict wake recovery, but is of interest to what
extent this is true, since the computational feasibility of 2-D simulations is
attractive.

>>>>

In this study we set out to model the wake of the University of New Hampshire's
Reference Vertical-Axis (cross-flow) Turbine (UNH-RVAT) using a
Reynolds-averaged Navier--Stokes numerical model. Though studies in the
literature generally focus on predicting the turbine loading and the local blade
boundary layer, we seek to model the larger scale flow produced by the rotor.
The wake of this particular turbine is of interest since it has been shown
experimentally that the near-wake's momentum and energy transport processes are
dominated by vertical advection \cite{Bachant2015-JoT}. It logically follows
that a 2-D simulation would not correctly predict wake recovery, but is of
interest to what extent this is true, since the computational feasibility of 2-D
simulations is attractive.
